Manuscript analyses

### 2022-07-07 ide_cel/Manuscript analyses.Rmd
Add multivariate analysis and forest plot

As discussed at meeting, rather than showing count recovery over time plan to show Grade 3+ cytopenias (Hb, Plt, ANC, WBC) over time (Day –5, Day +30, Day +60, Day +90)
**We want grade 3 only right?**
```{r}
# cart2 %>% 
#   select(PT,
#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
#   ) %>% 
#   pivot_longer(cols = `gr3_Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
#   group_by(name, value) %>% 
#   filter(!is.na(value)) %>% 
#   summarise(count=n()) %>% 
#   mutate(perc=(count/sum(count)*100)
#   ) %>% 
#   separate("name", into = c("gr3", "name", "day"), sep = "_") %>% 
#   filter(value == "YES") %>% 
#   # unite(time, c("day":"me"), sep = " ") %>% 
#   ggplot(aes(x= day, y= perc, fill= name))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   scale_fill_viridis_d() +
#   labs(fill = NULL, y = "%", title = "Grade 3+")+
#   theme_classic()
# 
# cart2 %>% 
#   select(PT,
#          `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
#          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
#          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
#          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
#          
#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
#   ) %>% 
#   pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
#   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
#          grade = case_when(
#            grade == "gr3_"       ~ "Grade 3+",
#            TRUE                  ~ "Any grade"
#          )) %>% 
#   mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
#          name2 = coalesce(name1, name)) %>% 
#   group_by(name2, value, grade) %>% 
#   filter(!is.na(value)) %>% 
#   summarise(count=n()) %>%
#   group_by(name2, grade) %>% 
#   mutate(perc=(count/sum(count)*100)
#   ) %>%
#   separate("name2", into = c("name", "day"), sep = "_") %>% 
#   filter(value == "YES") %>% 
#   # unite(time, c("day":"me"), sep = " ") %>% 
#   ggplot(aes(x= day, y= perc, fill= name, alpha= grade))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   scale_fill_viridis_d() + 
#   scale_alpha_ordinal(range = c(0.5, 1))+
#   labs(fill = NULL, y = "%")+
#   theme_classic()

@@

b <- a %>% filter(grade == "Any grade")
a %>% filter(grade == "Grade 3+") %>% 
  ggplot(aes(x= day, 
             y= perc, 
             fill= name, alpha= 1
             ))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9), data= b,
           aes(x= day, y= perc, fill= name), alpha= 0.4)+
  scale_fill_brewer(palette = "Spectral")+
  labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
  theme_classic()+
  scale_alpha_continuous(limits = c(0.4,1), breaks = c(0.4,1),
                         labels= c("Any Grade", "Grade 3+"))

a %>% filter(grade == "Grade 3+") %>% 
  ggplot(aes(x= day, 
             y= perc, 
             fill= name, 
             ))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9))+
  scale_fill_brewer(palette = "Spectral")+
  ylim(0, 100)+
  labs(fill = NULL, x= NULL, y = "%")+
  theme_classic()

a %>%
  ggplot(aes(x= grade, 
             y= perc, 
             fill= name,
             alpha= grade
             ))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9))+
  scale_fill_brewer(palette = "Spectral")+
  labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
  theme_classic()+
  scale_alpha_discrete(range = c(0.7, 1),
                       labels= c("Any Grade", "Grade 3+"))+
  facet_wrap(. ~ day)
```

@@

>>>>

As discussed at meeting, rather than showing count recovery over time plan to show Grade 3+ cytopenias (Hb, Plt, ANC, WBC) over time (Day –5, Day +30, Day +60, Day +90)
**We want grade 3 only right?**
```{r, fig.width=12, fig.height=7}
# cart2 %>% 
#   select(PT,
#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
#   ) %>% 
#   pivot_longer(cols = `gr3_Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
#   group_by(name, value) %>% 
#   filter(!is.na(value)) %>% 
#   summarise(count=n()) %>% 
#   mutate(perc=(count/sum(count)*100)
#   ) %>% 
#   separate("name", into = c("gr3", "name", "day"), sep = "_") %>% 
#   filter(value == "YES") %>% 
#   # unite(time, c("day":"me"), sep = " ") %>% 
#   ggplot(aes(x= day, y= perc, fill= name))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   scale_fill_viridis_d() +
#   labs(fill = NULL, y = "%", title = "Grade 3+")+
#   theme_classic()
# 
# cart2 %>% 
#   select(PT,
#          `Leukopenia_-5d`, Leukopenia_30d, Leukopenia_60d, Leukopenia_90d,
#          `Neutropenia_-5d`, Neutropenia_30d, Neutropenia_60d, Neutropenia_90d,
#          `Anemia_-5d`, Anemia_30d, Anemia_60d, Anemia_90d,
#          `Thrombocytopenia_-5d`, Thrombocytopenia_30d, Thrombocytopenia_60d, Thrombocytopenia_90d,
#          
#          `gr3_Leukopenia_-5d`, gr3_Leukopenia_30d, gr3_Leukopenia_60d, gr3_Leukopenia_90d,
#          `gr3_Neutropenia_-5d`, gr3_Neutropenia_30d, gr3_Neutropenia_60d, gr3_Neutropenia_90d,
#          `gr3_Anemia_-5d`, gr3_Anemia_30d, gr3_Anemia_60d, gr3_Anemia_90d,
#          `gr3_Thrombocytopenia_-5d`, gr3_Thrombocytopenia_30d, gr3_Thrombocytopenia_60d, gr3_Thrombocytopenia_90d
#   ) %>% 
#   pivot_longer(cols = `Leukopenia_-5d`: gr3_Thrombocytopenia_90d) %>% 
#   mutate(grade = str_match(name, "(gr3_)(.*)")[,2],
#          grade = case_when(
#            grade == "gr3_"       ~ "Grade 3+",
#            TRUE                  ~ "Any grade"
#          )) %>% 
#   mutate(name1 = str_match(name, "(gr3_)(.*)")[,3],
#          name2 = coalesce(name1, name)) %>% 
#   group_by(name2, value, grade) %>% 
#   filter(!is.na(value)) %>% 
#   summarise(count=n()) %>%
#   group_by(name2, grade) %>% 
#   mutate(perc=(count/sum(count)*100)
#   ) %>%
#   separate("name2", into = c("name", "day"), sep = "_") %>% 
#   filter(value == "YES") %>% 
#   # unite(time, c("day":"me"), sep = " ") %>% 
#   ggplot(aes(x= day, y= perc, fill= name, alpha= grade))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   scale_fill_viridis_d() + 
#   scale_alpha_ordinal(range = c(0.5, 1))+
#   labs(fill = NULL, y = "%")+
#   theme_classic()

@@

b <- a %>% filter(grade == "Any grade")
a %>% filter(grade == "Grade 3+") %>% 
  ggplot(aes(x= day, 
             y= perc, 
             fill= name, alpha= 1
             ))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9), data= b,
           aes(x= day, y= perc, fill= name), alpha= 0.4)+
  scale_fill_brewer(palette = "Spectral")+
  labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
  theme_classic()+
  scale_alpha_continuous(limits = c(0.4,1), breaks = c(0.4,1),
                         labels= c("Any Grade", "Grade 3+"))
####################################################################################################
# a %>% filter(grade == "Grade 3+") %>% 
#   ggplot(aes(x= day, 
#              y= perc, 
#              fill= name, 
#              ))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 4.5,
#             position = position_dodge(width=0.9)
#             )+
#   
#   scale_fill_brewer(palette = "Spectral")+
#   ylim(0, 100)+
#   labs(fill = NULL, x= NULL, y = "%")+
#   theme_classic(base_size = 14)

a %>% filter(grade == "Grade 3+") %>% 
  ggplot(aes(x= day, 
             y= perc, 
             fill= name, 
             ))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9))+
  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 5,
            position = position_dodge(width=0.9), vjust=-1.5
            )+

  scale_fill_brewer(palette = "Spectral")+
  ylim(0, 100)+
  labs(fill = NULL, x= NULL, y = "%")+
  theme_classic(base_size = 14)+
  theme(legend.position="bottom")

# a %>% filter(grade == "Grade 3+") %>% 
#   ggplot(aes(x= day, 
#              y= perc, 
#              fill= name, 
#              ))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 4.5,
#             position = position_dodge(width=0.9), fontface='bold'
#             )+
#   
#   scale_fill_brewer(palette = "Spectral")+
#   ylim(0, 100)+
#   labs(fill = NULL, x= NULL, y = "%")+
#   theme_classic(base_size = 14)

# a %>% filter(grade == "Grade 3+") %>% 
#   ggplot(aes(x= day, 
#              y= perc, 
#              fill= name, 
#              ))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 4.5,
#             position = position_dodge(width=0.9), color= "grey27"
#             )+
#   
#   scale_fill_brewer(palette = "Spectral")+
#   ylim(0, 100)+
#   labs(fill = NULL, x= NULL, y = "%")+
#   theme_classic(base_size = 14)

# a %>% filter(grade == "Grade 3+") %>% 
#   ggplot(aes(x= day, 
#              y= perc, 
#              fill= name, 
#              ))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 5,
#             position = position_dodge(width=0.9)
#             )+
#   
#   scale_fill_brewer(palette = "Spectral")+
#   ylim(0, 100)+
#   labs(fill = NULL, x= NULL, y = "%")+
#   theme_classic(base_size = 14)+
#   theme(legend.position="bottom")
# a %>%
#   ggplot(aes(x= grade, 
#              y= perc, 
#              fill= name,
#              alpha= grade
#              ))+
#   geom_bar(stat = "identity",
#            position=position_dodge(width=0.9))+
#   scale_fill_brewer(palette = "Spectral")+
#   labs(fill = NULL, alpha=NULL, x= NULL, y = "%")+
#   theme_classic()+
#   scale_alpha_discrete(range = c(0.7, 1),
#                        labels= c("Any Grade", "Grade 3+"))+
#   facet_wrap(. ~ day)
```

@@

## MVA
```{r}
cart3 <- cart2 %>% 
  filter(is.na(Not_evaluable_at_90days)) %>%
  mutate(gr3_cytopenia_30d = case_when(
    gr3_cytopenia_30d == "NO"    ~ 0,
    gr3_cytopenia_30d == "YES"   ~ 1
  )) %>% 
  mutate(gr3_cytopenia_90d = case_when(
    gr3_cytopenia_90d == "NO"    ~ 0,
    gr3_cytopenia_90d == "YES"   ~ 1
  )) %>% 
  mutate(
         CRS_grade2 = case_when(
           `Max CRS grade (0-5)` < 2                              ~ "No CRS or Grade < 2",
           `Max CRS grade (0-5)` >= 2                             ~ "Grade ≥2"),
         CRS_grade2 = factor(CRS_grade2, levels = c("No CRS or Grade < 2", "Grade ≥2"))
  )

# glm(gr3_cytopenia_30d ~ `High Marrow Burden? (yes=1, no=0)` + `gr3_cytopenia_-5d` + CRS_grade2 + `Steroid use (Yes=1, No=0)` + `Number of prior lines of therapy`,
#     data = cart3,
#     family = "binomial") %>%
#   tbl_regression(exponentiate = TRUE, 
#                  intercept = TRUE) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 30**") %>%
#   bold_p(t = .05) 
# 
# glm(gr3_cytopenia_90d ~ `High Marrow Burden? (yes=1, no=0)` + `gr3_cytopenia_-5d` + CRS_grade2 + `Steroid use (Yes=1, No=0)` + `Number of prior lines of therapy`,
#     data = cart3,
#     family = "binomial") %>%
#   tbl_regression(exponentiate = TRUE, 
#                  intercept = TRUE) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
#   bold_p(t = .05) 
# 
# glm(gr3_cytopenia_30d ~ `High Marrow Burden? (yes=1, no=0)` + CRS_grade2 + `Steroid use (Yes=1, No=0)` + `Number of prior lines of therapy`,
#     data = cart3,
#     family = "binomial") %>%
#   tbl_regression(exponentiate = TRUE, 
#                  intercept = TRUE) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 30**") %>%
#   bold_p(t = .05)

glm(gr3_cytopenia_90d ~ `High Marrow Burden? (yes=1, no=0)` + `gr3_cytopenia_-5d` + CRS_grade2 + `Steroid use (Yes=1, No=0)` + `Number of prior lines of therapy`,
    data = cart3,
    family = "binomial") %>%
  tbl_regression(exponentiate = TRUE, 
                 intercept = TRUE) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  modify_spanning_header(everything() ~ "**Grade 3+ Cytopenia at days 90**") %>%
  bold_p(t = .05) 
```

```{r}
forest_p <- 
  glm(gr3_cytopenia_90d ~ `High Marrow Burden? (yes=1, no=0)` + `gr3_cytopenia_-5d` + CRS_grade2 + `Steroid use (Yes=1, No=0)` + `Number of prior lines of therapy`,
    data = cart3,
    family = "binomial") %>%
  tbl_regression(exponentiate = TRUE) %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  fill(OR, `95% CI`, .direction = "up") %>% 
  filter(!str_detect(Characteristic, "YES|NO|CRS_grade2|No CRS")) %>% 
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
  mutate(name= c("High marrow burden (≥50%)",
                 "Grade ≥ 3 Cytopenia at Day -5",
                 "Grade ≥ 2 CRS",
                 "Steroid use",
                 "Number of prior lines of therapy"
                 ))

ggplot(data=forest_p, aes(y=name, x=OR, xmin=lower, xmax=upper)) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10(breaks = c(0, 0.25, 0.5, 1, 2.5, 5, 10, 40))+
  labs(y="")
```
